Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2019-12-02 xrb/paper.tex
Reformatting
add new plot

Figure~\ref{fig:10_10_overview} shows the temperature, energy
generation rate, and $w$ component of the velocity (the out-of-plane
velocity induced by the Coriolis force).  This latter field
illustrates the hurricane effect set up by the laterally spreading
burning front.  In the energy generation rate plot, we see that the
burning is mostly concentrated toward the bottom of the layer, as
expected since the density is greatest there.  We see that the peak of
the burning has moved off of the symmetry axis, demonstrating that the
burning front is propagating to the right.  In the temperature plot,
we see the effect of our refinement criteria focusing only on the part of
the atmosphere where we are most dense, with an artificial change in the
temperature at the refinement boundary due in part to the construction
of the initial model using the fine grid resolution for HSE. \MarginPar{Remind the reader what this
  was/where they should be looking in the plot to see this temperature
  drop} As we will see in the lower resolution case, we do not believe
that this affects the results.

@@

The final approximation to explore is our choice of rotation rate.
{\color{red} need to add discussion + plot}

>>>>

Figure~\ref{fig:10_10_overview} shows the temperature, energy
generation rate, and $w$ component of the velocity (the out-of-plane
velocity induced by the Coriolis force).  This latter field
illustrates the hurricane effect set up by the laterally spreading
burning front.  In the energy generation rate plot, we see that the
burning is mostly concentrated toward the bottom of the layer, as
expected since the density is greatest there.  We see that the peak of
the burning has moved off of the symmetry axis, demonstrating that the
burning front is propagating to the right.  In the temperature plot,
we see the effect of our refinement criteria focusing only on the part of
the atmosphere where we are most dense, with an artificial change in the
temperature at the refinement boundary due in part to the construction
of the initial model using the fine grid resolution for HSE. \MarginPar{Remind the reader what this
  was/where they should be looking in the plot to see this temperature
  drop} As we will see in the lower resolution case, this does not
affect the results.

@@

The final approximation to explore is our choice of rotation rate.  We
ran a simulation at 1000 Hz for 12.6~ms (shorter than the 20~ms we
used for the other runs).  We also used a larger domain, $1.8432\times
10^5~\mathrm{cm} \times 3.072\times 10^4~\mathrm{cm}$ to account for
the larger Rossby radius.  Figure~\ref{fig:10_10_slow} shows the flame
structure.  Overall it looks much like the faster rotator.  In the
next section, we explore the effect of rotation on the flame
acceleration.

\begin{figure}[t]
\centering
\plotone{flame_wave_slow}
\caption{\label{fig:10_10_slow} Temperature, mean molecular weight, energy generation rate, and out-of-plane velocity for the 10/10-1000 Hz simulation at 12.6~ms.}
\end{figure}
